Formalization of Abstract Rewriting

### 2025-02-21 Relations/Paper/Implications.tex
Update from WNFP to NP etc
WN and SM gets SN

    \begin{tikzpicture}[auto,
      arrowstyle/.style={->, line width=1pt, >={Latex[length=3mm, width=2mm]}, shorten >=2pt}]
      % A box style
      \tikzstyle{boxnode} = [draw, rectangle, text centered]

      % Place the nodes vertically (top to bottom)
      \node (Confluent) [boxnode] at (-4,0) {$\CR$};
      \node (RP)        [boxnode, right=.5cm of Confluent] {$\WMFP$};
      \node (WN)        [boxnode, right=.5cm of RP] {$\WNFP$};
      \node (UN)        [boxnode, right=.5cm of WN] {$\UNto$};

@@

        % Define the nodes
        \node (SN) [boxnode] at (4,0) {$\SN$};
        \node (WN) [boxnode, above right=0.5cm and 0.5cm of SN] {$\WN$};
        \node (SR) [boxnode, below right=0.5cm and 0.5cm of SN] {$\SM$};
        \node (WR) [boxnode, right of=SN, xshift=2cm] {$\WM$};

@@

\verb|SNdec→WN : (~R R) isMinDec → SN ⊆ WN| \footnote{ARS-Implications.agda}

@@

The following tables show which combination of these properties implies a property higher in the hierarchy. Where a combination 
does not imply a higher property a explanatory counterexample is given. The counterexamples referenced are in section \ref{sec:Counterexamples}.

The first table explores where the properties hold locally, the second explores where the properties hold globally, and the third 
table is global and includes the $\WCR$ property. An property being red indicates that classical assumptions are required for the implication 
to hold.

\sacomment{UPDATE COUNTEREXAMPLES WHEN CE SECTION FINISHED}
\begin{table}[h!]
    \centering
    \caption{Local implications}
    \begin{tabular}{|>{\columncolor{gray!30}}l|c|c|c|c|c|}
    \hline
    \rowcolor{gray!30}     & $\WM$         & $\WN$         & $\SM$             & $\SMandWN$        & $\SN$ \\
    \hline
    $\UNto$ &  CE-, CE-     & CE, CE-       & CE , CE-          & CE, CE            & \red{$\CR$} , $\SN$ \\
    \hline
    $\WNFP$ & CE-, CE-      & $\CR$, CE-    & CE , CE-          & $\CR$, $\SN$      & \red{$\CR$} , $\SN$ \\
    \hline
    $\WMFP$ & $\CR$ , CE-    & $\CR$, CE-    & \red{$\CR$} , CE- & $\CR$, $\SN$      & \red{$\CR$} , $\SN$ \\
    \hline
    $\CR$   & $\CR$, CE-     & $\CR$, CE-     & $\CR$, CE-        & $\CR$, $\SN$     & $\CR$ , $\SN$ \\
    \hline

    \end{tabular}
\end{table}

\begin{table}[h!]
    \centering
    \caption{Global implications}
    \begin{tabular}{|l|c|c|c|c|c|}
    \hline
            & $\WM$         & $\WN$         & $\SM$             & $\SMandWN$        & $\SN$ \\
    \hline
    $\UNto$ &  CE-, CE-     & $\CR$, CE-    & CE , CE-          & $\CR$, $\SN$      & \red{$\CR$} , $\SN$ \\
    \hline
    $\WNFP$ & CE-, CE-      & $\CR$, CE-    & CE , CE-          & $\CR$, $\SN$      & \red{$\CR$} , $\SN$ \\
    \hline
    $\WMFP$ & $\CR$ , CE    & $\CR$, CE-    & \red{$\CR$} , CE- & $\CR$, $\SN$      & \red{$\CR$} , $\SN$ \\
    \hline
    $\CR$   & $\CR$, CE     & $\CR$, CE     & $\CR$, CE-        & $\CR$, $\SN$      & $\CR$ , $\SN$ \\
    \hline

    \end{tabular}
\end{table}

\begin{table}[h!]
    \centering
    \caption{Global implications with global $\WCR$}
    \begin{tabular}{|l|c|c|c|c|c|}
    \hline
            & $\WM$         & $\WN$         & $\SM$             & $\SMandWN$        & $\SN$ \\
    \hline
    $\UNto$ &  CE-, CE-     & $\CR$, CE-    &  $\CR$ , CE-      & $\CR$, $\SN$      &  $\CR$ , $\SN$ \\
    \hline
    $\WNFP$ & CE-, CE-      & $\CR$, CE-    &  $\CR$ , CE-      & $\CR$, $\SN$      &  $\CR$ , $\SN$ \\
    \hline
    $\WMFP$ & $\CR$ , CE    & $\CR$, CE-    &  $\CR$ , CE-      & $\CR$, $\SN$      &  $\CR$ , $\SN$ \\
    \hline
    $\CR$   & $\CR$, CE     & $\CR$, CE     &  $\CR$, CE-       & $\CR$, $\SN$      & $\CR$ , $\SN$ \\
    \hline

    \end{tabular}
\end{table}

@@

The tables show that there are two changes when moving from properties holding locally and globally. 
Globally $\WN \land \UNto \implies \CR$ whereas it does not locally.

>>>>

    \begin{tikzpicture}[auto,
      arrowstyle/.style={->, line width=1pt, >={Latex[length=3mm, width=2mm]}, shorten >=2pt}]
      % A box style
      \tikzstyle{boxnode} = [draw, rectangle, text centered,minimum width=1.2cm, inner sep=3pt]

      % Place the nodes vertically (top to bottom)
      \node (Confluent) [boxnode] at (-4,0) {$\CR$};
      \node (RP)        [boxnode, right=.5cm of Confluent] {$\MP$};
      \node (WN)        [boxnode, right=.5cm of RP] {$\NP$};
      \node (UN)        [boxnode, right=.5cm of WN] {$\UNto$};

@@

        % Define the nodes
        \node (SN) [boxnode] at (4,0) {$\SN$};
        \node (WN) [boxnode, above right=0.5cm and 0.5cm of SN] {$\WN$};
        \node (SR) [boxnode, below right=0.5cm and 0.5cm of SN] {$\SM$};
        \node (WR) [boxnode, below right=0.5cm and 0.5cm of WN] {$\WM$};

@@

\verb|SNdec→WN : (~R R) isMinDec → SN ⊆ WN| \footnotemark[1]

@@

The following tables show which combination of these properties implies a property higher in the hierarchy. Where a combination 
does not imply a higher property an explanatory counterexample is given. The counterexamples referenced are in section \ref{sec:Counterexamples}.

The first table explores where the properties hold locally, the second explores where the properties hold globally. The proofs that the 
following implications hold are primarily found in \texttt{ARS-implications.agda} unless they have been proven as part of the formalization 
of \terese, in which case they will be found in either \texttt{ARS-thoerems.agda} or \texttt{ARS-NewmansLemma.agda}.

\sacomment{UPDATE COUNTEREXAMPLES WHEN CE SECTION FINISHED}
\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
\begin{table}[h!]
    \centering
    \caption{Local implications}
    \begin{tabular}{|>{\columncolor{gray!30}}l|c|c|c|c|c|}
    \hline
    \rowcolor{gray!30}     & $\WM$         & $\WN$         & $\SM$             & $\SMandWN$        & $\SN$ \\
    \hline
    $\UNto$ &  CE-, CE-     & CE, CE-       & $\CR$\footnotemark[1] , CE-          & $\CR$\footnotemark[1], CE            & $\CR$\footnotemark[2] , $\SN$ \\
    \hline
    $\NP$ & CE-, CE-      & $\CR$, CE-    & $\CR$\footnotemark[1] , CE-          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
    \hline
    $\MP$ & $\CR$ , CE-    & $\CR$, CE-    & $\CR$\footnotemark[2] , CE- & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
    \hline
    $\CR$   & $\CR$, CE-     & $\CR$, CE-     & $\CR$, CE-        & $\CR$, $\SN$     & $\CR$ , $\SN$ \\
    \hline

    \end{tabular}
\end{table}
\begin{table}[h!]
    \centering
    \caption{Global implications}
    \begin{tabular}{|>{\columncolor{gray!30}}l|c|c|c|c|c|}
    \hline
    \rowcolor{gray!30}     & $\WM$         & $\WN$         & $\SM$             & $\SMandWN$        & $\SN$ \\
    \hline
    $\UNto$ &  CE-, CE-     & $\CR$, CE-    & $\CR$\footnotemark[1] , CE-          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
    \hline
    $\NP$ & CE-, CE-      & $\CR$, CE-    & $\CR$\footnotemark[1] , CE-          & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
    \hline
    $\MP$ & $\CR$ , CE    & $\CR$, CE-    & $\CR$\footnotemark[2] , CE- & $\CR$, $\SN$      & $\CR$\footnotemark[2] , $\SN$ \\
    \hline
    $\CR$   & $\CR$, CE     & $\CR$, CE     & $\CR$, CE-        & $\CR$, $\SN$      & $\CR$ , $\SN$ \\
    \hline

    \end{tabular}
\end{table}
\footnotetext[1]{This implication also requires global $\WCR$.}
\footnotetext[2]{This implication also requires either global $\WCR$ or the classical property required to go from 
$\SN \to \WN$ or $\SM \to \WM$.}
\renewcommand*{\thefootnote}{\arabic{footnote}}

@@

The tables show that there are two changes when moving from properties holding locally to globally. 
Globally $\WN \land \UNto \implies \CR$ holds whereas it does not locally. Similarly, $\SM \land \WN \implies \SN$ holds 
globally but not locally.

Theorem 1.2.2 ii in \terese is the claim that $\WN \land \UN \implies \CR$ holds, and we formalize this in

\verb|ii : R isWN × R isUN → R isCR| \footnotemark[3]

We have modestly generalized this theorem by showing that $\WN \land \UNto \implies \CR$ holds (and indeed this is the basis for our proof of the theorem). 
Counterexample \sacomment{REF HERE} shows why this implication cannot hold when the properties are only local. Our proof is in the function:

\verb|UN→∧WN→CR : R isUN→ → R isWN → R isCR| \footnotemark[1]

To show that $\SM \land \WN \implies \SN$ we built on our proof that locally $\SM \land \WN \land \NP \implies \SN$. If $\WN$ applies 
globally then our proof no longer requires the property $\NP$. This progression of proofs can be seen in the functions:

\verb|WN∧NP∧SM→SN : ∀ {x} → WN x → NP x → SM x → SN x|

\verb|isWN∧SM→SN : R isWN → ∀ {x} → SM x → SN x|

\verb|isWN∧isSM→isSN : R isWN → R isSM → R isSN| \footnotemark[1]
